Reputational Risk and Questionable Research Practices in Archaeological Science

### 2023-10-12 README.Rmd
show docker badge

[![Docker build status](https://github.com/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/workflows/.github/workflows/render-in-docker.yml/badge.svg)](https://github.com/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/actions)

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/master?urlpath=rstudio)

>>>>

[![Docker build status](https://github.com/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/workflows/.github/workflows/render-in-docker.yaml/badge.svg)](https://github.com/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/actions) [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/wg-sociopolitics-of-knowledge-production-in-archaeology-workshop/master?urlpath=rstudio)

### 2023-10-12 docs/paper.qmd
show docker badge

# save this so we don't have to scrape again
saveRDS(ft_df,
        "data/full_text_jasr.rds")
```

@@

ft_df_jasr <- readRDS("data/full_text_jasr.rds")

>>>>

# save this so we don't have to scrape again
saveRDS(ft_df, here::here("data/full_text_jasr.rds"))
```

@@

ft_df_jasr <- readRDS(here::here("data/full_text_jasr.rds"))
